On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-05 paper.tex
Intro modified

\end{tikzpicture}
\caption{Upper bounds on the length of a conformation foldable by a deterministic unary oritatami system at delay $\delta$ and arity $\alpha$.
At any combination of delay and arity without anything written, no upper bound is known yet.
}
\label{fig:summary}
\end{figure}
In this paper, we will solve this problem partially at arity 1 in Sect.~\ref{sect:arity1} and completely at delay 1 in Sect.~\ref{sect:delay1}. 
Concretely speaking, we will prove that at arity 1 and delay 2 or 3, the upper bound is $(3n+1)(n+1)$. 
Upper bounds for longer delays remain open. 
At delay 1, we will provide a quadratic upper bound $3n(n+1)+1$ for the case of arity being 4, while a linear upper bound $4n+14$ for arity 3. 
At the delay 1 and arity 2, one infinite structure turns out to be foldable deterministically, which is the zigzag conformation shown in Fig.~\ref{TTT_zigzag}. 
These results as well as known upper bounds are summarized in Fig.~\ref{fig:summary}. 
As shown at the end of Sect.~\ref{sec:preliminaries}, the stabilization of first $t$ beads of transcript by a determinisitc oritatami system can be simulated by a deterministic Turing machine within $t^3$ steps (Corollary~\ref{cor:DTIME3}). 
Thus, the above mentioned upper bounds show that at delay 1 and arity 1, 3, or 4, or at delay 2 or 3 and arity 1, the class of deterministic unary oritatami systems is not Turing universal. 
The Turing universal oritatami system by Geary et al. \cite{GeMeScSe2018} employs more than 500 types of beads. 
Thus, this weakness result is not surprising at all. 
The unary oritatami system might not be practical very much, though one bead may abstarct an oligonucleotide (a short sequence of nucleotides), and in that case, unary transcript can be a repetitive but nonunary sequence, which is not so unrealistic in experiments (see \cite{GearyAndersen2014}). 
Nevertheless, this paper makes a first considerable step towards the characterization of non-Turing-universal oritatami systems.

@@

\section{Upper bounds for delay 1 or arity 1}

\input{arity1upper}
\input{tt_intro}
\input{tt_theorem}

>>>>

\end{tikzpicture}
\caption{Upper bounds on the length of a conformation foldable by a deterministic unary oritatami system at delay $\delta$ and arity $\alpha$.
At any combination of delay and arity without anything written, no upper bound is known yet.
}
\label{fig:summary}
\end{figure}
In this paper, we will solve this problem  completely at delay 1and partially at arity 1 in Sect.~\ref{sect:upper}. 
At delay 1, we will provide a quadratic upper bound $3n(n+1)+1$ for the case of arity being 4, while a linear upper bound $4n+14$ for arity 3. 
At the delay 1 and arity 2, one infinite structure turns out to be foldable deterministically, which is the zigzag conformation shown in Fig.~\ref{TTT_zigzag}. 
At arity 1, we will prove that at delay 2 or 3, the upper bound is $(3n+1)(n+1)$. 
Upper bounds for longer delays remain open. These results as well as known upper bounds are summarized in Fig.~\ref{fig:summary}. 
As shown at the end of Sect.~\ref{sec:preliminaries}, the stabilization of first $t$ beads of transcript by a determinisitc oritatami system can be simulated by a deterministic Turing machine within $t^3$ steps (Corollary~\ref{cor:DTIME3}). 
Thus, the above mentioned upper bounds show that at delay 1 and arity 1, 3, or 4, or at delay 2 or 3 and arity 1, the class of deterministic unary oritatami systems is not Turing universal. 
The Turing universal oritatami system by Geary et al. \cite{GeMeScSe2018} employs more than 500 types of beads. 
Thus, this weakness result is not surprising at all. 
The unary oritatami system might not be practical very much, though one bead may abstarct an oligonucleotide (a short sequence of nucleotides), and in that case, unary transcript can be a repetitive but nonunary sequence, which is not so unrealistic in experiments (see \cite{GearyAndersen2014}). 
Nevertheless, this paper makes a first considerable step towards the characterization of non-Turing-universal oritatami systems.

@@

\section{Upper bounds for determinisitc unary oritatami systems at delay 1 or arity 1}\label{sect:upper}

\input{tt_intro}
\input{tt_theorem}
\input{arity1upper}
